Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research

### 2023-12-10 manuscript/paper.Rmd
update

|-------------|---------------|---------------------------------------------|

@@

With the purpose of identifying influential variables impacting blood
pressure, a variable selection process was conducted. The initial
approach involved employing best subset selection with 10-fold
cross-validation to ascertain the optimal number of subsets. Notably,
for systolic blood pressure, the forward best subset selection method
discerned 13 variables, whereas diastolic blood pressure exhibited 19
selected variables. However, a limitation inherent in forward best
subset selection is its inability to eliminate previously selected
features, potentially disregarding their relevance in light of newly
added variables. Consequently, this methodology may yield suboptimal
variable selections due to its lack of adaptability.

@@

The univariate analysis of potential confounding factors is shown in
Table 2.

>>>>

|-----------------|-----------------|--------------------------------------|

@@

With the purpose of identifying influential variables impacting blood
pressure, a variable selection process was conducted. The initial
approach involved employing best subset selection with 10-fold
cross-validation to ascertain the optimal number of subsets. Notably,
for systolic blood pressure, the forward best subset selection method
discerned 13 variables, whereas diastolic blood pressure exhibited 19
selected variables. However, a limitation inherent in forward best
subset selection is its inability to eliminate previously selected
features, potentially disregarding their relevance in light of newly
added variables. Consequently, this methodology may yield sub-optimal
variable selections due to its lack of adaptability.

@@

The uni-variate analysis of potential confounding factors is shown in
Table 2.
